Parsing Postfix log files

### 2009-03-03 doc/logparser-architecture.tex
Wrote C-style comment parsing example for rule conditions. Tidied up in a couple of other places.

\newlength{\regexwidth}
% These figures come from experimentation; set the length to 0pt, see how
% big a hbox latex complains about, and then set the length.  Stupid latex
% cannot do \settowidth{\verb}.  Poo.
\setlength{\regexwidth}{130pt}
\newlength{\actionwidth}
\setlength{\actionwidth}{\textwidth}
\addtolength{\actionwidth}{-\regexwidth}
% This is the width of the number column, roughly.
\addtolength{\actionwidth}{-30pt}
% This is the overhead of space around columns, on either side, etc.
\addtolength{\actionwidth}{-24pt}

\begin{table}[ht]
    \caption{Regexes and Actions to calculate the weight of a chemical
    compound}
    \empty{}\label{Regexes and Actions to calculate the weight of a
    chemical compound}
    \begin{tabular}{lp{\regexwidth}p{\actionwidth}}

@@

@@

XXX STATEFUL PARSING ENABLED BY CONDITIONS, E.G\@.  PARSING C COMMENTS\@.

>>>>

% These figures come from experimentation; set the length to 0pt, see how
% big a hbox latex complains about, and then set the length.  Stupid latex
% cannot do \settowidth{\verb}.  Poo.
\newlength{\chemicalactionwidth}
\setlength{\chemicalactionwidth}{\textwidth}
% This is the width of the number column, roughly.
\addtolength{\chemicalactionwidth}{-30pt}
% The width of the regex column.
\addtolength{\chemicalactionwidth}{-130pt}
% This is the overhead of space around columns, on either side, etc.
\addtolength{\chemicalactionwidth}{-24pt}

\begin{table}[ht]
    \caption{Regexes and Actions to calculate the weight of a chemical
    compound}
    \empty{}\label{Regexes and Actions to calculate the weight of a
    chemical compound}
    \begin{tabular}{llp{\chemicalactionwidth}}

@@

An example of how rule conditions can be useful is parsing C-style
comments, which start with \texttt{/*} and end with \texttt{*/}; the start
and end tokens can be on one line, or may have many lines between them.
\Tableref{Rules to parse C-style comments} shows the regexes, conditions,
and state changes of the four rules required to parse C-style comments.
These rules are somewhat simplified, e.g.\ rules one and two will recognise
the comment start token even if it is within a quoted string, which is
incorrect.  Rules one and two will only be used when the parser is parsing
code, not comments: rule one recognises a comment that is contained within
one line and leaves the parser's state unchanged; rule two recognises the
start of a command and changes the parser's state to parsing comments.
Rules three and four will be used when the parser is parsing a comment:
rule three recognises the end of a comment and switches parsing state back
to parsing code; rule four recognises a comment line without an end token
and keeps the parser's unchanged.  It is important that the rules are
applied in the order listed in \tableref{Rules to parse C-style comments};
\sectionref{prioritisation and rule ordering} explains how this is
achieved.

\begin{table}[ht]
    \caption{Rules to parse C-style comments}
    \empty{}\label{Rules to parse C-style comments}
    \begin{tabular}{llll}
        \tabletopline{}%
        No.   & Regex             & Condition         & New State         \\
        \tablemiddleline{}%
        1     & \verb!/\*.*?\*/!  & state == code     & state = code      \\
        2     & \verb!/\*.*!      & state == code     & state = comment   \\
        3     & \verb!.*\*/!      & state == comment  & state = code      \\
        4     & \verb!.*!         & state == comment  & state = comment   \\
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@
